\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{sourcesanspro}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\pagestyle{empty}

% Define title format
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5em}{0.5em}

% Set font family
\renewcommand{\familydefault}{\sfdefault}

% Reduce space between list items
\setlist[itemize]{itemsep=0pt, topsep=0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Gustavo Gardusi}} \\[1.00em]
    {\small
        \begin{minipage}{0.75\textwidth}
        \href{https://github.com/gardusig}{github.com/gardusig} \hfill
        \href{mailto:gustavo.gardusi@gmail.com}{gustavo.gardusi@gmail.com} \hfill
        \href{https://www.linkedin.com/in/gardusig}{linkedin.com/in/gardusig}
    \end{minipage}}
\end{center}

\section*{Work Experience}

\textbf{Amazon Web Services (AWS)}
    \hfill Vancouver, BC, Canada
    \\ Software Development Engineer II
    \hfill \textit{May 2025 – Sep 2025}
\begin{itemize}
    \item Expanded \textbf{Amazon Connect} to support Tokyo and Osaka, providing \textbf{automated traffic redirection} during \textbf{outages}.
    \item Updated \textbf{workflows} to \textbf{replicate resources} to a new paired region, \textbf{triggered} on event-driven \textbf{stack changes}, with automatic DNS records propagation. Used CDK, CloudFormation, Route 53, EventBridge, Step Functions, Aurora PostgreSQL.
\end{itemize}

\textbf{Amazon Web Services (AWS)}
    \hfill Sao Paulo, SP, Brazil 
    \\ Software Development Engineer II
    \hfill \textit{Nov 2024 – May 2025}
\begin{itemize}
    \item Enhanced the internal \textbf{game asset release tool} with asynchronous \textbf{queue consumption} and \textbf{front-end poll} for progress.
    \item Launched the \textbf{Skill Builder} public \textbf{profile page}, displaying user \textbf{progress data} from \textbf{game-based learning} modules, with a beautiful UI built in Tailwind CSS and TypeScript. Used Cognito, CloudFront, API Gateway, Lambda, SQS, DynamoDB.
    \item Enabled users to \textbf{share achievements} on \textbf{LinkedIn} with a badge \textbf{image preview} through server-rendered meta tags.
\end{itemize}

\textbf{Orkes}
    \hfill Cupertino, CA, USA (Remote)
    \\ Software Engineer (contractor)
    \hfill \textit{Jan 2022 – Jul 2023}
\begin{itemize}
    \item Created \textbf{cross-language SDKs} (Python, Go, Java, C\#, JavaScript) for the Conductor \textbf{workflow orchestration} platform. Standardized interfaces and documentation with examples, delivered core features with automated integration tests.
    \item Improved workflow \textbf{throughput} by \textbf{20\%} with a \textbf{long-running thread pool} per \textbf{worker}, to periodically \textbf{poll} for workflow \textbf{tasks} in \textbf{batches}, then start a thread per polled task, to process and upload results, making \textbf{parallel} HTTP/gRPC \textbf{requests}.
    \item Contributed to \textbf{\href{https://github.com/Netflix/conductor/commit/a13706fc78a3dc040593fd06ae6d9bfc8a7768cf}{Netflix OSS}} by adding \textbf{missing} message \textbf{acknowledgment requests} after \textbf{batch requests} on the server.
\end{itemize}

\textbf{Amazon (.com.br)}
    \hfill Sao Paulo, SP, Brazil 
    \\ Software Development Engineer II
    \hfill \textit{Apr 2021 – Jan 2022}
\begin{itemize}
    \item Resized the \textbf{EC2 fleet} for \textbf{invoice services} ahead of \textbf{Black Friday} using the expected \textbf{peak usage} and the \textbf{maximum requests} a single \textbf{host} could \textbf{sustain} on average. Based on historical \textbf{load tests} integrated into the deployment pipeline.
    \item Extended Java \textbf{microservices} and the React \textbf{UI} to show state-specific \textbf{invoice expiration dates} for \textbf{FBA sellers} in \textbf{Brazil}.
    \item Created targeted \textbf{alarms} and a concise \textbf{runbook}, with a \textbf{cleanup script} to reduce on-call tickets, using \textbf{disk usage metrics}.
\end{itemize}

\textbf{Beyond}
    \hfill Sao Paulo, SP, Brazil 
    \\ Software Engineer (contractor)
    \hfill \textit{Sep 2019 – Apr 2021}
\begin{itemize}
    \item Built a \textbf{matching engine} to reproduce \textbf{stock exchange behavior} with FIX and to validate \textbf{strategies} through \textbf{backtests}.
    \item Maintained a \textbf{HFT} application running during trading day, to \textbf{send} hundreds of \textbf{orders} per second. Used C++, WebSocket.
    \item Implemented Java \textbf{APIs} and Python \textbf{ETL} to \textbf{receive} 1 GB of daily \textbf{stock market data}. Used API Gateway, Lambda, and S3.
\end{itemize}

\textbf{Algar (Telecom)}
    \hfill Uberlandia, MG, Brazil 
    \\ Software Engineer
    \hfill \textit{Oct 2017 – Sep 2019}
\begin{itemize}
    \item Built Python \textbf{scripts} to periodically \textbf{query} hundreds of router's \textbf{metadata} and keep the SQL database \textbf{up to date}.
    \item Introduced \textbf{parallel execution} of router management \textbf{commands}, improving \textbf{operational efficiency} by 80\%.
\end{itemize}

\section*{Education}

\textbf{Federal University of Uberlandia} 
    \hfill Uberlandia, MG, Brazil
    \\Bachelor of Science in Computer Science (Incomplete)
    \hfill \textit{2014 – 2022}
\begin{itemize}
    \item Focused on algorithms and data structures; strong \textbf{problem-solving} foundations.
\end{itemize}

\section*{Awards \& Competitive Programming}
\begin{itemize}
    \item \textbf{\href{https://icpc.global/ICPCID/SP7WIXMME8B8}{ICPC}:} 4× Latin America Regional \textbf{Finalist}; highest rank: \textbf{16th/1,000+} teams.
    \item \textbf{Hacker Cup:} 3× placed in the top \textbf{2,000} worldwide (\href{https://www.facebook.com/codingcompetitions/hacker-cup/2023/certificate/490890632182886}{2023}, \href{https://www.facebook.com/codingcompetitions/hacker-cup/2022/certificate/490890632182886}{2022}, \href{https://www.facebook.com/codingcompetitions/hacker-cup/2021/certificate/490890632182886}{2021}); best: \textbf{467/30,000+}.
    \item \textbf{\href{https://www.codechef.com/users/gardusig}{CodeChef}} | \textbf{\href{https://codeforces.com/profile/gardusig}{Codeforces} | \href{https://leetcode.com/u/ggardusi/}{LeetCode}:} Ranked in the top \textbf{10\%} worldwide among \textbf{100,000+} users.    
\end{itemize}

\end{document}
