\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=0.66in]{geometry}
\usepackage{enumitem}
\usepackage{sourcesanspro}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\linespread{0.96}
\pagestyle{empty}

% Define title format
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1.5em}{0.5em}

% Set font family
\renewcommand{\familydefault}{\sfdefault}

% Reduce space between list items
\setlist[itemize]{itemsep=0pt, topsep=0pt}

% Begin document
\begin{document}

% Name and contact information
\begin{center}
    {\LARGE \textbf{Gustavo Gardusi}} \\[0.5em]
    {\small \href{mailto:gustavo.gardusi@gmail.com}{gustavo.gardusi@gmail.com} \textbar \href{https://github.com/gardusig}{github.com/gardusig} \textbar \href{https://www.linkedin.com/in/gardusig}{linkedin.com/in/gardusig} }
\end{center}

% Experience
\section*{Work Experience}

\textbf{Amazon (AWS)}
    \hfill Vancouver, BC, Canada
    \\ Software Development Engineer II 
    \hfill \textit{May 2025 - Present}
\begin{itemize}
    \item Expanded Amazon Connect’s global region distribution by enabling deployment in new Asia-Pacific regions.
\end{itemize}

\textbf{Amazon (AWS)}
    \hfill São Paulo, SP, Brazil 
    \\ Software Development Engineer II 
    \hfill \textit{Nov 2024 – May 2025}
\begin{itemize}
    \item Launched the AWS Skill Builder public profile from Figma to a responsive UI. Built with React (CloudFront) and Java/Python (API Gateway, Lambda, SQS, DynamoDB) through CDK-managed infrastructure.
    \item Scaled the internal game asset release tool with asynchronous workflows and front-end polling.
\end{itemize}

\textbf{Orkes}
    \hfill Cupertino, CA, USA (Remote from Brazil)
    \\ Software Engineer
    \hfill \textit{Jan 2022 – Dec 2023}
\begin{itemize}
    \item Created SDKs for Conductor — a microservice orchestration platform originally open-sourced by Netflix — in Python, Go, Java, C\#, and JavaScript. Delivered core features, tests, documentation, and usage examples.
    \item Designed a batch processing and parallel worker model that improved workflow task throughput by 20\%.
\end{itemize}

\textbf{Amazon (.com.br)}
    \hfill São Paulo, SP, Brazil 
    \\ Software Development Engineer II 
    \hfill \textit{Apr 2021 – Jan 2022}
\begin{itemize}
    \item Integrated load-testing into two invoice services pipeline to block underperforming builds, and scaled EC2 hosts ahead of Black Friday by simulating traffic with historic API distributions.
    \item Onboarded over 2,000 FBA sellers by extending Java APIs to handle Brazilian state-specific tax regulations. 
\end{itemize}

\textbf{Beyond}
    \hfill São Paulo, SP, Brazil 
    \\ Software Engineer
    \hfill \textit{Sep 2019 – Apr 2021}
\begin{itemize}
    \item Built a high-frequency trading engine in C++ to process millions of daily orders using WebSocket and FIX.
    \item Implemented Java APIs and Python ETL to transform real-time stock market data (API Gateway, Lambda, EC2, S3).
\end{itemize}

\textbf{Algar (Telecom)}
    \hfill Uberlandia, MG, Brazil 
    \\ Software Engineer
    \hfill \textit{Oct 2017 – Sep 2019}
\begin{itemize}
    \item Built Python scripts to periodically query hundreds of routers and update a SQL database.
    \item Introduced parallel execution of router management commands, improving operational efficiency by 90\%.
\end{itemize}

% Education
\section*{Academic Background}

\textbf{Federal University of Uberlandia} 
    \hfill Uberlandia, MG, Brazil
    \\Bachelor of Science in Computer Science
    \hfill \textit{2014 – 2020}
\begin{itemize}
    \item Focused on algorithms, data structures, and competitive programming (60\% completed).
\end{itemize}

% Awards
\section*{Competitive Programming}
\begin{itemize}
    \item \textbf{Meta HackerCup:} 3× Top 2,000 globally (T-shirt winner); Best placement: 467th out of 30,000+ participants.
    \item \textbf{Codeforces / CodeChef:} Top 10\% globally (Candidate Master); Ranked among 100,000+ users.
    \item \textbf{ICPC:} 4× Latin America Regional Finalist; Best placement: 16th out of 1,000+ teams.
\end{itemize}

\end{document}
